---
title: "prob3.cp1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
dados <- read.csv("emendas_detalhes_parlamentar.csv")
dados <- select(dados,VALOR_REPASSE_PROPOSTA_EMENDA,TIPO_PARLAMENTAR,UF_PROPONENTE,NATUREZA_JURIDICA,ANO_PROP,DESC_ORGAO,MODALIDADE,NM_PROPONENTE,OBJETO_PROPOSTA,funcao.imputada)
summary(dados)
dados.sumarise.gByTipoParlamentar <- summarise(group_by(dados,TIPO_PARLAMENTAR,NM_PROPONENTE),TOTAL=sum(VALOR_REPASSE_PROPOSTA_EMENDA))
dados.sumarise.gByUF.tipo_parlamentar <- summarise(group_by(dados,UF_PROPONENTE,TIPO_PARLAMENTAR),TOTAL=sum(VALOR_REPASSE_PROPOSTA_EMENDA))
dados.sumarise.gByUF.ano <- summarise(group_by(dados,UF_PROPONENTE,ANO_PROP),TOTAL=sum(VALOR_REPASSE_PROPOSTA_EMENDA))
dados.sumarise.gByAno.Uf <- summarise(group_by(dados,ANO_PROP,UF_PROPONENTE),TOTAL=sum(VALOR_REPASSE_PROPOSTA_EMENDA))
```

## Descrição dos Dados
Foi usado os dados detalhados  <https://github.com/nazareno/ciencia-de-dados-1/blob/master/dados/emendas_detalhes_parlamentar.csv.tgz>.
As variavies para uma exploração previas foram escolhidas(VALOR_REPASSE_PROPOSTA_EMENDA,TIPO_PARLAMENTAR,UF_PROPONENTE,NATUREZA_JURIDICA,ANO_PROP,DESC_ORGAO,MODALIDADE,NM_PROPONENTE,OBJETO_PROPOSTA,funcao.imputada) levando em consideração seu significado para o problema.

```{r plotsummary}
bp <- ggplot(dados.sumarise.gByUF.tipo_parlamentar,aes(UF_PROPONENTE,TOTAL))
bp + geom_boxplot() + coord_flip()
bp <- ggplot(dados.sumarise.gByAno.Uf,aes(as.factor(ANO_PROP),TOTAL))
bp + geom_boxplot()
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
